Kindly Bent to Free Us

### 2020-03-04 kindly/extensions.tex
NLL Extension: made it more clear that this is not currently implemented in Affe.

Such code patterns are dynamically safe since $a$ is not used after
the second line.
Non-lexical lifetimes handle this by removing expressions
that do not mention $a$ from its region; in this example,  the
expression on the last line.
%
In \lang, regions are purely lexical and marked by the
expression $\region{b}{e}$.
During inference, we introduce kind constraint to prevent escaping from
a region.

We can replace the lexical region by
an annotation on each expression indicating which borrows are live
in this expression.
When exploring a subexpression, we compare the annotations, and automatically
apply the $\textsc{Region}$ rule when they differ.
%
This approach is equivalent to inlining the $\textsc{Region}$ rule in all the other
rules.

Applied to the program above, only the first two lines would be annotated
to be ``in the region associated with @&x@'', but not the last line.
Thanks to these annotations, when type checking the sequence we check
that the borrow does not escape the left-hand side (i.e., the second line).

>>>>

Such code patterns are dynamically safe since $a$ is not used after
the second line.
Non-lexical lifetimes handle this by removing expressions
that do not mention $a$ from its region; in this example,  the
expression on the last line.
%
In \lang, regions are purely lexical and marked by the
expression $\region{b}{e}$.
During inference, we introduce kind constraints to prevent escaping from
a region.

To add support for non-lexical lifetimes, we could replace the
lexical region by an annotation on each expression indicating which borrows are
live in this expression.
When exploring a subexpression, we would compare the annotations, and automatically
apply the $\textsc{Region}$ rule when they differ.
%
This approach is equivalent to inlining the $\textsc{Region}$ rule in all the other
rules.

Applied to the program above, only the first two lines would be annotated
to be ``in the region associated with @&x@'', but not the last line.
Thanks to these annotations, when type checking the sequence we would check
that the borrow does not escape the left-hand side (i.e., the second line).
